---
title: "Ch 10 More Data Verbs"
author: "Yaowen Tan"
date: "2021/3/1"
output: html_notebook
---

Assigned Exercises
DC Chapter 10 Exercises: 10.1-10.7

```{R}
rm(list = ls())

# packages in use
library(tidyverse)
library(dcData)
data("BabyNames")

```


## Problem 10.1

1 Summary Function

2 Data Verbs

3 Transfomation

4 Reduction Function

5 Data Verbs

6 Data Verbs
 
7 Data Verbs

8 Data Verbs



## Problem 10.2

1 mutate()

2 Arrange() and Desc()

3 Filter()

4 Select()

5 Filter() and Rank()


## Problem 10.3

1 nrow()

2 ncol() 

3 help()

4 library()

5 group_by()

## Problem 10.4

1 Arrange()
```{r}
library(dplyr)  
BabyNames %>%
  arrange((count))
```

2 
```{r}
BabyNames %>%
  filter(sex == "F")
```

3 Filter()
```{r}
BabyNames %>%
  filter(sex == "M")
```

4 summarise()

```{r}
BabyNames %>%
  summarize(total = sum(count))
```

5 Select()
```{r}
BabyNames %>%
  select(name, count)
```

## Problem 10.5

1
```{r}
library(dplyr)  
data("Minneapolis2013", package = "dcData")
 Minneapolis2013 %>%
  group_by(First, Second, Third, Precinct, Ward) %>%
  filter(First==Second, First!=Third)%>%
  summarise(total = n())%>%
  arrange(desc(total))
```

1 274 people
2 Mark Andrew, Undervote, and ABDUL M RAHAMAN "THE ROCK".
3 Undervote


```{r}
data("Minneapolis2013", package = "dcData")
 Minneapolis2013 %>%
  group_by(First, Second, Third, Precinct, Ward) %>%
  filter(First=="OLE SAVIOR", First!=Third)%>%
  summarise(total = n())%>%
  arrange(desc(total))
```

## Problem 10.6
```{r}
#data("diamonds")
diamonds %>% 
  group_by(color) %>% 
  summarise_at(vars(carat), list(Carat_Color_mean = mean))
```
1, J

```{r}
#data("diamonds")
diamonds %>% 
  group_by(clarity) %>% 
  summarise_at(vars(table), list(table_clarity_mean = mean))
```

2  I1 has the largest table per carat.



## Problem 10.7 
```{r}
Minor<-
  Minneapolis2013 %>%
  group_by(First) %>%
  summarise(count=n()) %>%
  mutate(First = if_else(condition = (count < 5000), true = "minor", false= First))
show(Minor)
```

```{r}
library(tidyverse)
library(dcData)
library(mosaicData)
data(CPS85)
CPS85 %>%
 ggplot(aes(x = age, y = wage)) %>%
 geom_point()
```
222
1112
